---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# EasySentiment

<!-- badges: start -->
<!-- badges: end -->

The goal of EasySentiment is to provide for an easy way to do simple sentiment analysis quickly. Conducting basic sentiment analysis can be fairly easy but it can involve many steps that could be confusing to someone inexperinced or unfamiliar with the technichal details. This package will provide a function to create a sentiment analysis function that will allow the user to choose from a few sentiment dictionaries. It will also provide a function to visulaize the sentimetns with a few options. Overall, this will provide someone with little technichal know how the ability to conduct a basic sentiment analysis. 

## How to Install

```{r}


```

## Example of get_sentiments()
```{r}
library(EasySentiment)

example_strings <- c("I am really angry right now", "I am very very happy", "Rage and mixed feelings", "i lied")
example_sentiments <- get_sentiments(example_strings, "bing")



```

